Data Encryption Standard Implementation 4003-482-01 RIT \\ Team BitShift

### 2010-05-06 paper/paper.tex
Noted compiler optimization levels

\section{Original Runtime Measurements}
\paragraph{}Each test consisted of 1,000,000 encryptions of the message 123456789ABCDEF and key 133457799BBCDFF1. They were performed on a 1.8 Ghz Core2Duo computer running Ubuntu 10.04.

@@

\section{Revised Runtime Measurements}
\paragraph{}Each test consisted of 1,000,000 encryptions of the message 123456789ABCDEF and key 133457799BBCDFF1. They were performed on a 1.8 Ghz Core2Duo computer running Ubuntu 10.04.
\begin{multicols}{4}
Test 1:  5.960 sec

>>>>

\section{Original Runtime Measurements}
\paragraph{}Each test consisted of 1,000,000 encryptions of the message 12 34 56 78 9A BC DE F and key 13 34 57 79 9B BC DF F1. They were performed on a 1.8 Ghz Core2Duo computer running Ubuntu 10.04. The times were made with level 2 compiler optimiz
ation. Our profiling data had all compiler optimization turned off.

@@

\section{Revised Runtime Measurements}
\paragraph{}Each test consisted of 1,000,000 encryptions of the message 12 34 56 78 9A BC DE F and key 13 34 57 79 9B BC DF F1. They were performed on a 1.8 Ghz Core2Duo computer running Ubuntu 10.04. The times were made with level 2 compiler optimization. Our profiling data had all compiler optimization turned off.
\begin{multicols}{4}
Test 1:  5.960 sec
